04_DESeq_sexes

### 2019-09-04 analysis/04_DESeq2_sexes.Rmd
now with annotated image
now with PRL-related genes

f <- LDAplot.hypothesis(LDA.gon2 , "Gonad model 3", "parental stage ~ .  has 0.368 pred. acc.",
                        "LD1, F = 6.029069", "LD2, F = 3.837591")

@@

>>>>

f <- LDAplot.hypothesis(LDA.gon2 , "Gonad model 2", "parental stage ~ .  has 0.368 pred. acc.",
                        "LD1, F = 6.029069", "LD2, F = 3.837591")

@@

## plot genes in a  PRL WGCNA module

```{r wgcna, eval = T, fig.width=5.25, fig.height=3}
plotWGCNAcandidates(vsd.pit, c("NP_990797.2"), colDataPit, "PRL expression")

plotWGCNAcandidates(vsd.pit,
                    c("NP_990797.2","NP_001004392.2", "NP_001004403.1", "NP_001006255.2", "NP_001006274.1",
                           "NP_989500.1", "XP_001234815.2", "XP_015149152.1", "XP_416110.5"),
                    colDataPit, "9 of 102 genes in a WGCNA module containting gene of interest")

plotWGCNAcandidates(vsd.pit,
                    c("XP_428110.3","NP_001004392.2",  "XP_015142961.1", "XP_015139636.1",
                      "XP_015137408.1", "XP_004938696.1", "NP_990620.1", "NP_001170793.2", "NP_001026250.1"),
                    colDataPit, "Prolaction receptor: 9 of 147 genes in a WGCNA module containting PRLR")
```
